The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-28 paper.tex
update

\subsection{Inclined jet injection}
  Recent paper \citep{Gallimore2006} has proposed that\
  there is a lack of preferred orientation of jets with respect to the plane of the disc.\
  There are a number of galaxies in which the jets are inclined to the disc normal\
  (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
  including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

  Motivated by these observations, we simulate three different inclined angles
  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane to\
  release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of inclined angle on the shape of bubbles.

  The jet is constantly ejected from a cylindrical source with
  four-velocity

  the density contrast between the thermal gas contained in the jets
  and the ambient gas

@@

>>>>

\subsection{Inclined jet injection}
  Early observation \citep{Gallimore2006} has proposed that\
  there is a lack of preferred orientation of jets with respect to the plane of the disc.\
  There are a number of galaxies in which the jets are inclined to the disc normal\
  (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
  including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

  Motivated by these observations, we simulate three different inclined angles,\
  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane\
  in order to release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of the jet-disk misalignment on the symmetry of bubbles.

  All three cases with different inclined angles share the same injection parameters:\
  the density contrast between the thermal gas contained in the jet source and the ambient gas,\
  $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
  the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
  the CR energy density $e_{\text{CR}}=??$,\
  and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
  along the symmetric axis of cylinder.

  Note that as we inject the jets within the clumpy disk,\
  we define the ambient gas density by the peak density of\
  the isothermal disk on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

  Jet power Eddington luminosity

  The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
  with diameter and height of 4 pc, leading to the volume $\sim 50 \text{pc}^{3}$,\
  much smaller than that of individual clump by a factor of 83.\
  By intentionally reducing the ratio of the volume of jet source and of clump,\
  we

@@

  Source size is much smaller than clump
